Clean data

### 2018-03-20 01_clean-data.Rmd
Dichotomize everything

results_file <- file.path(here(), "Data", "test_data.csv")

@@

@@

                                  Favorable = "Very favorable")))

>>>>

# Calculate the quantile (and median) of an ordered factor
# Borrowed from @jrnold: https://gist.github.com/jrnold/6759254
#
# In the case of ties, the first in order will win. For instance, 
# bloop <- factor(c("A", "A", "B", "B"), ordered = TRUE)
# median(bloop)  # "A"
quantile.ordered <- function(x, probs = seq(0, 1, 0.25)) {
  tab <- table(x)
  cdf <- cumsum(tab / sum(tab))
  idx <- sapply(probs, function(p) min(which(cdf >= p)))
  levels(x)[idx] 
}

quantile.factor <- quantile.ordered
median.ordered <- function(x) quantile(x, 0.5)
median.factor <- median.ordered

# Load data
results_file <- file.path(here(), "Data", "test_data.csv")

@@

         volunteer = factor(volunteer, levels = c("No", "Yes"), ordered = TRUE),

@@

                                  Favorable = "Very favorable"))) %>% 
  mutate(give_charity_3 = fct_recode(give_charity,
                                     `At least once a month` = "Once a week",
                                     `At least once a month` = "Once a month",
                                     `Once a month-once a year` = "Once every three months",
                                     `Once a month-once a year` = "Once every six months",
                                     `Once a month-once a year` = "Once a year",
                                     Rarely = "Once every few years",
                                     Rarely = "Never") %>% fct_rev()) %>% 
  mutate(political_knowledge_bin = fct_recode(political_knowledge,
                                              `Often` = "Most of the time",
                                              `Often` = "Some of the time",
                                              `Not often` = "Only now and then",
                                              `Not often` = "Hardly at all") %>% fct_rev()) %>% 
  mutate(ideology_3 = fct_recode(ideology,
                                 `Liberal` = "Strong liberal",
                                 `Liberal` = "Liberal",
                                 `Liberal` = "Independent, leaning liberal",
                                 `Independent` = "Independent",
                                 `Conservative` = "Independent, leaning conservative",
                                 `Conservative` = "Conservative",
                                 `Conservative` = "Very conservative") %>% fct_rev()) %>% 
  mutate(ideology_bin = fct_recode(ideology_3,
                                   `Not liberal` = "Independent",
                                   `Not liberal` = "Conservative")) %>% 
  mutate(education_bin = fct_recode(education,
                                    `No BA` = "Less than high school",
                                    `No BA` = "High school graduate",
                                    `No BA` = "Some college",
                                    `No BA` = "2 year degree",
                                    `BA and above` = "4 year degree",
                                    `BA and above` = "Graduate or professional degree",
                                    `BA and above` = "Doctorate")) %>% 
  mutate(religiosity_bin = fct_recode(religiosity,
                                      `At least once a month` = "More than once a week",
                                      `At least once a month` = "Once a week",
                                      `At least once a month` = "Once or twice a month",
                                      `Rarely` = "A few times a year",
                                      `Rarely` = "Seldom",
                                      `Rarely` = "Never",
                                      NULL = "Don't know") %>% fct_rev()) %>% 
  mutate(income_clean = fct_recode(income, NULL = "Prefer not to say"),
         income_bin = factor(income_clean >= median(.$income), levels = c(FALSE, TRUE),
                             labels = paste(c("Less than", "At least"), median(.$income)))) %>% 
  mutate(age_bin = factor(age >= median(.$age), levels = c(FALSE, TRUE),
                          labels = paste(c("Less than", "At least"), median(.$age))))
